One Year HPC Certification Forum in Retrospective

### 2019-04-17 paper.tex
edited the training delivery section

We encourage the development of an ecosystem around the HPC classification, we are supporting training and tool development.

@@

Firstly, an author of training material is allowed to indicate on the training material itself or on promotional material the fact
which skills are covered by the material completely or partially.
We provide a seal that can be used for that purpose (see \Cref{fig:seal-teaching}).
The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material
registers a link to the material or course on our webpage using an online form. %\footnote{Details of the link will show the email address.}
That way, the HPCCF is informed about the usage of the seal.

Secondly, we will link on our webpage the endorsed training material for the individual skills and certificates.
By using JavaScript and dynamic webpage we will provide various views on the skills with and without links to suitable training materials.

Note that we are not intending to verify the correct usage of the skill explicitly.
However, in case the training material or course doesn't deliver the expected material practitioners may complain and we will remove the training material from our webpage.

We expect that this strategy will lead to the availability of good free training material for most skills while companies and individuals can still charge for effective training courses.
Ultimately, the resulting training material will complement each other leading to a rich variety of content suitable for each individual practitioner, e.g., addressing different learning styles and languages.

>>>>

The Forum encourages the development of an ecosystem around the HPC classification by supporting training and tool development. Many of its members are involved in those activities in a professional capacity, so the development of training materials and tools, and the development of the certification program have elements of co-design in them.

@@

Firstly, an author is allowed to indicate on the training material itself or a related promotional material which skills are covered either fully or partially.
We provide a seal that can be used for that purpose (see \Cref{fig:seal-teaching}).
The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material registers a link to the material or course on our webpage using an online form. %\footnote{Details of the link will show the email address.}
That way, the HPCCF is informed about the usage of the seal.

Secondly, we will link from our webpage the endorsed training material covering the individual skills and certificates.
By using JavaScript and dynamic webpage we will provide various views of the skills -- with and without links to suitable training materials.

Note that we are not intending to verify the correct usage of the seal explicitly.
However, in case the training material or course doesn't deliver the expected material practitioners may complain and we will remove the link to that training material from our webpage.

We expect that this strategy will make a good range of free training material available for most skills, while various institutions and individuals can still charge for effective training courses.
Ultimately, the catalogued training materials will complement each other, leading to a rich variety of content suitable for each individual practitioner, e.g., addressing different learning styles and languages. This becomes increasingly important as more in-time personalised training in needed by our ever-growing HPC community.
